Use of management strategy evaluation to inform in fisheries management in a changing climate

### 2019-08-22 Poster_ICES.Rmd
Draft objectives section

1. Pick a template layout.
2. Write/ create your poster content distraction free.
3. Let posterdown do its thing!

>>>>

Adaptive management arose to address uncertainties and accelerate progress towards meeting management objectives. With an eye towards adaptive management, we seek to note the lessons learned from successful MSEs to:

* Highlight unique aspects of MSEs that model climate change as a driver
* Identify shortcomings in MSE documentation that delays learning
* Identify aspects of successful MSEs that can be adopted to inform fisheries management in a changing climate

Need climate change imagery

Need MSE imagery

Need learning and adaptive management imagery
